%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,10pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{sectsty}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!80!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}
\sectionfont{\Large}
\subsectionfont{\large}
\usepackage{titlesec}

\renewcommand\labelitemi{--}


\usepackage[left=0.4in, right=0.4in, bottom=0.35in, top=0.35in]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}

%\newcommand{\note}[1]{\textcolor{red}{\,(#1)}}
\newcommand{\note}[1]{}

\usepackage{setspace}
\renewcommand{\baselinestretch}{0.94} 

\titlespacing*{\section}{0px}{6px}{4px}
\titlespacing*{\subsection}{0pt}{6px}{8px}
\titlespacing*{\paragraph}{0pt}{6px}{8px}

\input{glyphtounicode}

\pdfgentounicode=1

\begin{document}
{\raggedleft

\begin{minipage}[c]{0.28\textwidth}
	\begin{flushleft}
	\href{mailto:nil.mamano@gmail.com}{nil.mamano@gmail.com}\\
	1710 Dunlavy St\\
	Houston, Texas 77006, US\\
	832-212-3511
	\end{flushleft}
\end{minipage}\hfill
\begin{minipage}[c]{0.3\textwidth}
	\begin{center}
		\Huge{\textbf{Nil Mamano}}
	\end{center}
\end{minipage}\hfill
\begin{minipage}[c]{0.3\textwidth}
	\begin{flushright}
	\href{http://www.nmamano.com}{nmamano.com} \\
	\href{http://www.github.com/nmamano}{github.com/nmamano} \\
	\href{http://www.linkedin.com/in/nmamano}{linkedin.com/in/nmamano}
	\end{flushright}
\end{minipage}\\
\vspace{5px}
\hrulefill
}

\vspace{7px}
\noindent\textbf{Summary} Strong Computer Science fundamentals and problem-solving skills from doing research in algorithm design. Strong communication skills from collaborating with researchers and teaching. Quick learner looking forward to dive into the latest technologies.
\vspace{-12px}
\section*{Education}
\paragraph*{PhD + Masters in Computer Science} University of California Irvine, GPA 3.83/4 \hfill Sep 2015 -- Dec 2019
\paragraph*{B.E. in Computer Science} Polytechnic University of Catalonia, GPA 3.8/4 (99th percentile) \hfill Sep 2011 -- Jul 2015
\vspace*{-1px}
%\begin{itemize}[leftmargin=15px]
%	\item 2nd highest GPA in a cohort of 400+ students.
%\end{itemize}

\section*{Skills}
\textbf{Languages:} C++, C, Python, Java, HTML, CSS, Javascript, Bash, SQL~
\textbf{Tools:} Git, Github, Linux, Oracle Grid Engine.

\section*{Experience}
\subsection*{University of California Irvine}
\vspace{-3px}
\paragraph*{PhD Student Researcher} \hfill Sep 2015 -- Dec 2019

\vspace{-1px}
\begin{itemize}[leftmargin=15px]
	\item Co-authored 9 peer-reviewed articles on algorithm design.
	\item Designed data structures for matching drivers and passengers on a road network dynamically. Leveraged the topology of road networks to optimize the data structures and scale them to statewide networks with 100k+ edges. [Java]   
	\item Led a research project: came up with an original research problem, engaged 3 colleagues to work on it, and collaborated with them to solve it, write a paper, and get it published. We designed an optimal algorithm for the knight tour problem. [Javascript]
	\item Designed clustering algorithms for partitioning data into balanced clusters, and applied them to gerrymandering prevention: they can partition a geographic region into compact and equal-population districts. Built a desktop application with a GUI to visualize and benchmark the algorithms. [C++, OpenGL, Javascript]
	\item Improved the runtime of the multi-fragment algorithm for Euclidean TSP from $O(n^2)$ to $O(n\log n)$.
%	\item Designed a parallel algorithm for DNA sequencing.
	%\item Proved that a class of Greedy algorithms can be computed in a distributed system.
	%\item Implemented an algorithm for embedding hidden ``watermarks'' in large graphs by hiding information in the structure of the graphs, allowing companies to share data encoded as graphs such as social networks without the risk of it being leaked. [Python]
\end{itemize}

\paragraph*{Teaching Assistant} \hfill Sep 2016 -- Jun 2018

\vspace{-1px}
\begin{itemize}[leftmargin=15px]
	\item 100+ sessions teaching algorithms to groups of 50+ students, with excellent student evaluations.
	\item Championed the use of online automated grading to provide immediate feedback to the students and reduce the grading load. Led a study with 100+ students to measure the effect of automated grading.
\end{itemize}
\paragraph*{Undergrad Researcher} \hfill Feb 2015 -- Jul 2015

\vspace{2px}
\noindent Created SANA, a biological network alignment software that uses simulated annealing to predict the function of proteins. Ran large-scale experiments in a computing cluster to fine-tune the algorithm and managed to outperform the leading algorithms in accuracy and runtime simultaneously. [C++, Bash, Oracle Grid Engine]
	 
\vspace{3px}
\subsection*{Polytechnic University of Catalonia}
\vspace{-2px}
\paragraph*{Research Intern} \hfill Feb 2014 -- Sep 2014

\vspace{2px}
\noindent Contributed to RACSO, a free online judge (automated grading tool) for compiler and automata theory courses. Built an interpreter for a C-like language used by the students to write their solutions, following Test-driven development. [C++]
		%\item Prepared 70+ online exercises, and exams taken by 100+ students.

\section*{Selected projects}
Built an efficient in-memory key-value Cache that supports timeouts, using templates and C++17 features. It implements Redis' algorithm to remove expired entries and has an LRU eviction mechanism. [C++]

\section*{Selected publications}
\begin{itemize}[leftmargin=15px]
\item ``Euclidean TSP, Motorcycle Graphs, and Other New Applications of Nearest-Neighbor Chains'' N. Mamano, A. Efrat, D. Eppstein, D. Frishberg, M.T. Goodrich, S. Kobourov, P. Matias, V. Polishchuk, International Symposium on Algorithms and Computation 2019
\item ``Stable-Matching Voronoi Diagrams: Combinatorial Complexity and Algorithms'' G. Barequet, D. Eppstein, M. T. Goodrich, and N. Mamano, International Colloquium on Automata, Languages and Programming 2018
\item ``Reactive Proximity Data Structures for Graphs'' D. Eppstein, M.T. Goodrich, and N. Mamano, Latin American Theoretical Informatics Symposium 2018
\item ``SANA: Simulated Annealing far outperforms many other search algorithms for biological network alignment'' N. Mamano and W. Hayes, Bioinformatics: Oxford Journals 2017
\end{itemize}


\end{document}


%\section*{Awards and Honors}
%\begin{itemize}
%	\item Balsells Graduate Fellowship\hfill 2015 -- 2016
%	\item Balsells Fellowship---Undergraduate Mobility Program\hfill 2014
%	\item Formula Santander International Scholarship \hfill 2014
%\end{itemize}
